---
title: "Untitled"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
# titanic is avaliable in your workspace
# 1 - Check the structure of titanic
str(titanic)

# 2 - Use ggplot() for the first instruction
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position ="dodge")

# 3 - Plot 2, add facet_grid() layer
ggplot(titanic, aes(x = Pclass, fill = Sex)) +
  geom_bar(position ="dodge")+
  facet_grid(.~ Survived)

# 4 - Define an object for position jitterdodge, to use below
posn.jd <- position_jitterdodge(0.5, 0, 0.6)

# 5 - Plot 3, but use the position object from instruction 4

ggplot(titanic, aes(x = Pclass,y=Age, color = Sex)) +
  geom_point(size=3,alpha=0.5,position=posn.jd)+
  facet_grid(.~ Survived)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
